---
title: "Efficient R and Parallelization - 1"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
gradethis_setup()
```

## foreach and doParallel

This function finishes in a little bit more than **two seconds** in parallel (due to the overhead setting up the parallel workers and collecting the results) and in about six seconds sequentially.

Change it so that it runs in parallel using `foreach()` and the parallel adaptor from the `doParallel` package.

```{r foreach, exercise=TRUE, eval=FALSE}
vec = c(2, 2, 2)
system.time({
  for (i in vec) {
    Sys.sleep(i)
  }
})
```

```{r foreach-hint-1, eval=FALSE}
[...]
# register the parallel backend
registerDoParallel(<cores>)
[...]
```

```{r foreach-hint-2, eval=FALSE}
[...]
# register the parallel backend
foreach(i = vec) %dopar% {
[...]
```

```{r foreach-solution}
library(foreach)
library(doParallel)
registerDoParallel(3)
system.time({
  foreach(i = vec) %dopar% {
    Sys.sleep(i)
  }
})
```

```{r foreach-check}
# debug_this()
grade_this({
  # fail_if(!"future_walk" %in% .user_code)
  pass_if(.result["elapsed"] < 3)
  grade_this_code(action = "fail")
  fail()
})
```

<!-- <div id="foreach-hint-1"> -->
<!-- You might want to limit the amount of cores used instead of using all available. -->
<!-- </div> -->

<!-- <div id="foreach-hint-2"> -->
<!-- You need to define a parallel cluster using {doParallel} to register your workers. -->
<!-- </div> -->

## foreach and doFuture

This function finishes in a little bit more than **two seconds** in parallel (due to the overhead setting up the parallel workers and collecting the results) and in about six seconds sequentially.

Change it so that it runs in parallel using `foreach()` and the parallel adaptor from the `doFuture` package.

```{r doFuture, exercise=TRUE, eval=FALSE}
vec = c(2, 2, 2)
system.time({
  for (i in vec) {
    Sys.sleep(i)
  }
})
```

```{r doFuture-hint-1, eval=FALSE, results='asis'}
After registering the future cluster, do not forget to initialize a {future} plan
```

```{r doFuture-solution, eval=FALSE}
library(foreach)
library(doFuture)
vec = c(2, 2, 2)

registerDoFuture()
plan(multisession, workers = 3)

system.time({
  foreach(i = vec) %dopar% {
    Sys.sleep(i)
  }
})
```

```{r doFuture-check}
grade_this({
  pass_if(.result["elapsed"] < 3)
  grade_this_code(action = "fail")
  fail()
})
```
